### 2020-03-30 papers.tex
papers.tex: Assign remaining reviews to papers (special thanks to Jenny!)
papers.tex: Garbage collect vaporware paper
papers.tex: Add Siva's ToC title
papers.tex: Cover naughty papers' page numbers

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{TODO: Craft a clever but cumbersome heading}

@@

\addtrack
	{}{SIGBOVIK}
\addpaper
	{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}
	{Shalin Shah}
	{Keywords: COVID-19, SIGBOVIK, lazy, quality, sadness, big Oof}
	{SIGBOVIK_2020_paper_36}
	{0cm}
	{}
\addpaper
	{Is this the longest Chess game?}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chesses, chessing, G.\@ K.\@ Chesterton}
	{SIGBOVIK_2020_paper_28}
	{0cm}
	{}
\addpaper
	{Optimizing the SIGBOVIK 2018 speedrun}
	{leo60228}
	{Keywords: speedrun, SIGBOVIK, pathfinding, DFS, Rust}
	{SIGBOVIK_2020_paper_20}
	{0cm}
	{}
\addpaper
	{Retraction of a boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{Keywords: groove, in, retraction, the}
	{SIGBOVIK_2020_paper_18}
	{0cm}
	{}

@@

\addtrack
	{}{Systems}
\addpaper
	{SIGBOVIK '75 technical note: Conditional move for shell script acceleration}
	{Dr.\@ James McCann, Dr.\@ Tom Murphy VII}
	{Keywords: cond-, itional, move}
	{SIGBOVIK_2020_paper_32}
	{0cm}
	{}
\addpaper
	{NaN-gate synthesis and hardware deceleration}
	{Cassie Jones}
	{Keywords: hardware deceleration, hardware synthesis, electronic design automation, IEEE-754, NaN-gates, cat meme}
	{SIGBOVIK_2020_paper_19}
	{0cm}
	{}
\addpaper
	{hbc: A celebration of undefined behavior}
	{Andrew Benson}
	{Keywords: compilers, undefined behavior, Bash misuse, computer music, Principles of Imperative Computation}
	{SIGBOVIK_2020_paper_34}
	{0cm}
	{}

@@

\addtrack
	{}{Security}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\addpaper
	{Putting the ceremony in ``authentication ceremony''}
	{Camille Cobb, Sruti Bhagavatula}
	{Keyword: authentication, ceremony, fun, security, weddings}
	{SIGBOVIK_2020_paper_23}
	{0cm}
	{}

\addtrack
	{}{Artificial Intelligence \& Machine Learning}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	{SIGBOVIK_2020_paper_6}
	{0cm}
	{}
\addpaper
	{Robot ethics:\@ Dangers of reinforcement learning}
	{Jake Olkin}
	{Keywords: deep reinforcement learning, ethics, simulation, spoof}
	{SIGBOVIK_2020_paper_24}
	{0cm}
	{}
\addpaper
	{Learning to be wrong via gradient ascent: A broken clock is right twice a day, but a clock that runs backwards can be used to tell the time!}
	{Alex Meiburg}
	{Keywords: machine learning, gradient descent, loss landscape, logistic regression, biased estimators, eliminating bias, overtraining}
	{SIGBOVIK_2020_paper_35}
	{0cm}
	{}
\addpaper
	{GradSchoolNet:\@ Robust end-to-end *-shot unsupervised deepAF neurla attention model for convexly optimal (artifically intelligent) success in computer vision research}
	{Divam Gupta, Varun Jain}
	{Keywords: none, haha, nono}
	{SIGBOVIK_2020_paper_17}
	{0cm}
	{}

\addtrack
	{}{Natural Intelligence \& Human Learning}
\addpaper
	{Sorting with human intelligence}
	{Cole Kurashige}
	{Keywords: sorting, algorithm, crowd sourcing, human intelligence}
	{SIGBOVIK_2020_paper_22}
	{0cm}
	{}
\addpaper
	{Synthesizing programs by asking people for help online}
	{Cassie Jones}
	{Keywords: program synthesis, cloud computing, social computation, the real program synthesizer was the friends we made along the way}
	{SIGBOVIK_2020_paper_15}
	{0cm}
	{}
\addpaper
	{HonkFast, PreHonk, HonkBack, PreHonkBack, HERS, AdHonk and AHC:\@ The missing keys for autonomous driving}
	{Bernhard Egger, Max Siegel}
	{Keywords: awesome paper, best paper award, great reviewer 3, awesome reviewer 2, marvelous reviewer 1}
	{SIGBOVIK_2020_paper_27}
	{0cm}
	{}

@@

\addtrack
	{}{The SIGBOVIK 2020 Field Guide to Conspiracy Theories}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{0cm}
	{}
\addpaper
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{0cm}
	{}

\addtrack
	{}{Serious Business}
\addpaper
	{The SIGBOVIK 2020 field guide to plants}
	{Jim McCann (editor)}
	{Keywords: field guide, plants, to}
	{SIGBOVIK_2020_paper_31}
	{0cm}
	{}
\addpaper
	{Deep industrial espionage}
	{Samuel Albanie, James Thewlis, Sebastien Ehrhardt, Jo\~ao F.\@ Henriques}
	{Keywords: late, very late, so extremely late}
	{SIGBOVIK_2019_paper_43}
	{0cm}
	{}
\addpaper
	{What is the best game console?: A free-market--based approach}
	{Dr.\@ Tom ``I Only Write Chess Papers Now'' Murphy VII Ph.D.}
	{Keywords: invisible hand, handheld console, minimum of 3 keywords}
	{SIGBOVIK_2020_paper_30}
	{0cm}
	{}

@@

\addpaper
	{Training ImageNet in 1 second: Early stopping theoretical accelerate training}
	{Yiping Lu, Denny Wu}
	{Keywords: optimization, deep learning, machine learning theory}
	% TODO
	{../message-from-committee}
	{0cm}
	{}

% TODO
\addreview{SIGBOVIK_2020_review_3}{0cm}
\addreview{SIGBOVIK_2020_review_4}{0cm}
\addreview{SIGBOVIK_2020_review_6}{0cm}
\addreview{SIGBOVIK_2020_review_9}{0cm}
\addreview{SIGBOVIK_2020_review_10}{0cm}
\addreview{SIGBOVIK_2020_review_11}{0cm}
\addreview{SIGBOVIK_2020_review_12}{0cm}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Table of COVID-tense}

@@

\addtrack
	{}{SIGBOVIK}
\addpaper
	{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}
	{Shalin Shah}
	{Keywords: COVID-19, SIGBOVIK, lazy, quality, sadness, big Oof}
	{SIGBOVIK_2020_paper_36}
	{0cm}
	{}
\addpaper
	{Is this the longest Chess game?}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chesses, chessing, G.\@ K.\@ Chesterton}
	{SIGBOVIK_2020_paper_28}
	{0cm}
	{}
\addpaper
	{Optimizing the SIGBOVIK 2018 speedrun}
	{leo60228}
	{Keywords: speedrun, SIGBOVIK, pathfinding, DFS, Rust}
	{SIGBOVIK_2020_paper_20}
	{0cm}
	{}
\addpaper
	{Retraction of a boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{Keywords: groove, in, retraction, the}
	{SIGBOVIK_2020_paper_18}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_9}{0cm}

@@

\addtrack
	{}{Systems}
\addpaper
	{SIGBOVIK '75 technical note: Conditional move for shell script acceleration}
	{Dr.\@ James McCann, Dr.\@ Tom Murphy VII}
	{Keywords: cond-, itional, move}
	{SIGBOVIK_2020_paper_32}
	{0cm}
	{}
\addpaper
	{NaN-gate synthesis and hardware deceleration}
	{Cassie Jones}
	{Keywords: hardware deceleration, hardware synthesis, electronic design automation, IEEE-754, NaN-gates, cat meme}
	{SIGBOVIK_2020_paper_19}
	{0cm}
	{}
\addpaper
	{hbc: A celebration of undefined behavior}
	{Andrew Benson}
	{Keywords: compilers, undefined behavior, Bash misuse, computer music, Principles of Imperative Computation}
	{SIGBOVIK_2020_paper_34}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_3}{0cm}

@@

\addtrack
	{}{Security}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_6}{0cm}
\addpaper
	{Putting the ceremony in ``authentication ceremony''}
	{Camille Cobb, Sruti Bhagavatula}
	{Keyword: authentication, ceremony, fun, security, weddings}
	{SIGBOVIK_2020_paper_23}
	{0cm}
	{}

\addtrack
	{}{Artificial Intelligence \& Machine Learning}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	{SIGBOVIK_2020_paper_6}
	{0cm}
	{}
\addpaper
	{Robot ethics:\@ Dangers of reinforcement learning}
	{Jake Olkin}
	{Keywords: deep reinforcement learning, ethics, simulation, spoof}
	{SIGBOVIK_2020_paper_24}
	{0cm}
	{}
\addpaper
	{Learning to be wrong via gradient ascent: A broken clock is right twice a day, but a clock that runs backwards can be used to tell the time!}
	{Alex Meiburg}
	{Keywords: machine learning, gradient descent, loss landscape, logistic regression, biased estimators, eliminating bias, overtraining}
	{SIGBOVIK_2020_paper_35}
	{0cm}
	{}
\addpaper
	{GradSchoolNet:\@ Robust end-to-end *-shot unsupervised deepAF neurla attention model for convexly optimal (artifically intelligent) success in computer vision research}
	{Divam Gupta, Varun Jain}
	{Keywords: none, haha, nono}
	{SIGBOVIK_2020_paper_17}
	{1.8cm}
	{}
\addreview{SIGBOVIK_2020_review_10}{0cm}

\addtrack
	{}{Natural Intelligence \& Human Learning}
\addpaper
	{Sorting with human intelligence}
	{Cole Kurashige}
	{Keywords: sorting, algorithm, crowd sourcing, human intelligence}
	{SIGBOVIK_2020_paper_22}
	{0cm}
	{}
\addpaper
	{Synthesizing programs by asking people for help online}
	{Cassie Jones}
	{Keywords: program synthesis, cloud computing, social computation, the real program synthesizer was the friends we made along the way}
	{SIGBOVIK_2020_paper_15}
	{0cm}
	{}
\addpaper
	{HonkFast, PreHonk, HonkBack, PreHonkBack, HERS, AdHonk and AHC:\@ The missing keys for autonomous driving}
	{Bernhard Egger, Max Siegel}
	{Keywords: awesome paper, best paper award, great reviewer 3, awesome reviewer 2, marvelous reviewer 1}
	{SIGBOVIK_2020_paper_27}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_11}{0cm}

@@

\addtrack
	{}{The SIGBOVIK 2020 Field Guide to Conspiracy Theories}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{0cm}
	{}
\addpaper
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_4}{0cm}

\addtrack
	{}{Serious Business}
\addpaper
	{The SIGBOVIK 2020 field guide to plants}
	{Jim McCann (editor)}
	{Keywords: field guide, plants, to}
	{SIGBOVIK_2020_paper_31}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_12}{0cm}
\addpaper
	{Deep industrial espionage}
	{Samuel Albanie, James Thewlis, Sebastien Ehrhardt, Jo\~ao F.\@ Henriques}
	{Keywords: late, very late, so extremely late}
	{SIGBOVIK_2019_paper_43}
	{1.8cm}
	{}
\addpaper
	{What is the best game console?: A free-market--based approach}
	{Dr.\@ Tom ``I Only Write Chess Papers Now'' Murphy VII Ph.D.}
	{Keywords: invisible hand, handheld console, minimum of 3 keywords}
	{SIGBOVIK_2020_paper_30}
	{0cm}
	{}

@@
